Results

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected citation

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022; @Westbrook2013; @Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, we reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: $$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, we reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: $$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
